Forecasting Gamma-Ray Bursts using Gravitational Waves

### 2018-08-29 Paper/Manuscript.tex
ERC Acknowledged

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}

@@

\acknowledgements 
I am grateful to Conor O'Toole for endless feedback and Niels Warburton, Richard A. Matzner and Alberto Sesana for reviewing this manuscript.

>>>>

@@

\acknowledgements 
I acknowledge support by the EU H2020 under ERC Starting Grant, no. BinGraSp-714626.
I am additionally grateful to Conor O'Toole for endless feedback and Niels Warburton, Richard A. Matzner, and Alberto Sesana for reviewing this manuscript.
